---
title: "Assignment_9"
author: "anders sorenson"
date: "3/27/2022"
output: html_document
---
```{r setup, include=FALSE}
library(tidyverse)
library(modelr)
library(ggplot2)
library(performance)
df <- read_csv("C:/Users/ander/Desktop/Data_Course_ANDERSSORENSON/Data/GradSchool_Admissions.csv")
```
Glimpse of the Data

```{r}
glimpse(df)


```
Visulaization shows a positive relationship between GRE and beign admitted same with GPA as would be expected.
```{r}
mod1 <- lm(admit ~ gre, data = df)
df = add_predictions(df,mod1,var = "mod1_Prediction")
df %>% 
  ggplot(aes(x = gre, y = mod1_Prediction)) + 
  geom_point()

mod2 <- lm(admit ~ gpa, data = df)
df = add_predictions(df,mod2,var = "mod2_Prediction")
df %>% 
  ggplot(aes(x = gpa, y = mod2_Prediction)) + 
  geom_point()

mod3 <- lm(admit ~ rank, data = df)
df = add_predictions(df,mod3,var = "mod3_Prediction")
df %>% 
  ggplot(aes(x = rank, y = mod3_Prediction)) + 
  geom_col()


```
Rank 2 schools seem to have the most number of students admitted to grad school

Now we look at models that contain multiple variables
```{r}
mod4 <- lm(admit ~ gre + gpa, data = df)
df = add_predictions(df,mod4,var = "mod4_Prediction")

mod5 <- lm(admit ~ gpa + rank, data = df)
df = add_predictions(df,mod5,var = "mod5_Prediction")

mod6 <- lm(admit ~ gre + rank, data = df)
df = add_predictions(df,mod6,var = "mod6_Prediction")

mod7 <- lm(admit ~ gre + rank + gpa, data = df)
df = add_predictions(df,mod7,var = "mod7_Prediction")

```
compare the models performance to one another using the performance package
```{r}
comps <- compare_performance(mod4,mod5,mod6,mod7,
                        rank = TRUE)
comps
```
This indicates that model 7, the model that includes rank, gpa , and gre is the most accurate predictor